A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-19 tex/codatadp.tex
more

The calculus consists of derivation rules that operate on a set $\Ec$ of
equalities and disequalities between $\Sig$-terms, where $\Ec$ is interpreted
as a conjunction.
We write $\tEc$ to denote the set of $\Sig$-terms occurring in $\Ec$.
%We will commonly denote tuples of terms $( t_1, \ldots, t_n )$ in bold font, as $\vec t$.
We assume that all $\Sig$-terms in $\Ec$ are \emph{normalized}, meaning that all subterms of the form $\const{s}^{\,k}_j( \const{C}_j(t_1,\ldots,t_n) )$
are simplified to $t_i$, and moreover assume that all %additional
constraints added to $\Ec$ are normalized in this manner.

@@

We present the calculus in three steps.
In the first step, we compute the bidirectional closure of $\Ec$;
in the second step, we make inferences based on cyclicity and bisimilarity;
and in the third step, %(when necessary),
we branch on constructor types for various terms in $\tEc$.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we call an application of it \emph{nonterminal}),
or is $\bot$ (in which case we call an application of it \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes nondeterministic branching.

>>>>

The calculus consists of derivation rules that operate on a set $\Ec$ of
equalities and disequalities between $\Sig$-terms, where $\Ec$ is interpreted
as a conjunction.
We write $\tEc$ to denote the set of $\Sig$-terms occurring in $\Ec$.
%We will commonly denote tuples of terms $( t_1, \ldots, t_n )$ in bold font, as $\vec t$.
We assume that all $\Sig$-terms in $\Ec$ are \emph{normalized}, meaning that all subterms of the form $\const{s}^{\,k}_j( \const{C}_j(t_1,\ldots,t_n) )$
are simplified to $t_k$. All constraints added to $\Ec$ are also implicitly
normalized in this manner.

@@

The calculus consists of three sets of rules corresponding to three
successive phases.
The first phase computes the bidirectional closure of $\Ec$.
The second phase makes inferences based on cyclicity (for datatypes)
and bisimilarity (for codatatypes).
The third phase performs case splitting on constructors
for various terms in $\tEc$.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we call an application of it \emph{nonterminal}),
or is $\bot$ (in which case we call an application of it \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes nondeterministic branching.
